Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
Outline of section on representations
surface

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
\newcommand{\indeg}{\mathrm{indeg}} % in-degree
\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
%\newcommand{\tai}{\mathsf{tai}} % target incompatible
%\newcommand{\tac}{\mathsf{tac}} % target compatible
%\newcommand{\soi}{\mathsf{soi}} % source incompatible
%\newcommand{\soc}{\mathsf{soc}} % source compatible
%\newcommand{\cso}{\mathsf{cso}} % cosource
%\newcommand{\cta}{\mathsf{cta}} % cotarget

@@

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
\begin{itemize}
\item it enters crossing an edge~$e_1$ and leaves crossing an edge~$e_2$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are consecutive on the boundary of~$f$,
\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
\end{definition}

@@

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
\end{definition}

@@

It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver,
and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}

@@

\begin{proof}
 The duality gives a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and induces a bijection~$\alpha\in (Q_\dissection)_1\mapsto \alpha\dual\in (Q_{\dissection\dual})_1$ with~$s(\alpha\dual)=s(\alpha)\dual$ and~$t(\alpha\dual)=t(\alpha)\dual$.
 Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
\end{proof}

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$. The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
\end{definition}

@@

\section{Pseudomanifolds}

In this section, we show that the non-kissing complex is a \defn{pseudomanifold},~\ie
\begin{enumerate}[(i)]
\item \defn{pure}: all maximal non-kissing simplices have the same number of walks as~$\dissection$, and
\item \defn{thin}: any codimension~$1$ simplex of~$\NKC$ is contained in exactly two maximal non-kissing simplices.
\end{enumerate}

\vincent{Peut-on utiliser une projection d'une alg\`ebre ammass\'ee ? Apparement non... On peut avoir le Koszul dual d'une alg\`ebre ammass\'ee.}

>>>>

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\blinkers}[1]{_{\LEFTCIRCLE \!\! #1 \!\! \RIGHTCIRCLE}} % blossom
\newcommand{\indeg}{\mathrm{indeg}} % in-degree
\newcommand{\outdeg}{\mathrm{outdeg}} % out-degree
%\newcommand{\tai}{\mathsf{tai}} % target incompatible
%\newcommand{\tac}{\mathsf{tac}} % target compatible
%\newcommand{\soi}{\mathsf{soi}} % source incompatible
%\newcommand{\soc}{\mathsf{soc}} % source compatible
%\newcommand{\cso}{\mathsf{cso}} % cosource
%\newcommand{\cta}{\mathsf{cta}} % cotarget
\newcommand{\Enrs}[1]{E_{nr}^{s}(#1)}
\newcommand{\Ers}[1]{E_{r}^{s}(#1)}
\newcommand{\Enrt}[1]{E_{nr}^{t}(#1)}
\newcommand{\Ert}[1]{E_{r}^{t}(#1)}

@@

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
\begin{itemize}
\item it enters crossing an edge~$e_1$ and leaves crossing an edge~$e_2$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are consecutive on the boundary of~$f$,
\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions.
\end{definition}

@@

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms.
\end{definition}

@@

It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver,
and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
\vincent{Explain also that we can get the blossoming quiver using the blossom points.}

@@

@@

We now associate a surface to a locally gentle bound quiver.

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the orientable surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{itemize}
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v]$, $\Enrt{\alpha} = [v, t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual]$ and~$\Ert{\alpha} = [v\dual, t(\alpha)]$ (colored red) as follows:
\vincent{Figure}
\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\alpha)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{itemize}
The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
\end{definition}

\begin{example}
\vincent{TODO.}
\end{example}

@@
